13th International Satisfiability Modulo Theories Competition (SMT-COMP 2018): Rules and Procedures

### 2019-03-22 rules/rules19.tex
rules 2019: Update submission information.

For participation in SMT-COMP, a solver must be uploaded to StarExec
and made publicly available.  StarExec supports solver configurations;
for clarity, \emph{each submitted solver must have one configuration
  only}.  Moreover, the organizers must be informed of the solver's
presence \emph{and the tracks and divisions in which it is
  participating} via the web form at
\begin{center}
  \url{https://goo.gl/forms/3pAMFHsfDJqGqucR2}
\end{center}
A submission must also include a 32-bit unsigned integer.  These
integer numbers, collected from all submissions, are used to seed the
benchmark scrambler.

\header{System description.}
%
As part of a submission, SMT-COMP entrants are strongly encouraged to
provide a short (1--2 pages) description of the system.  This should
include a list of all authors of the system, their present
institutional affiliations, and any appropriate acknowledgements.  The
programming language(s) and basic SMT solving approach employed should
be described (e.g., lazy integration of a Nelson-Oppen combination
with SAT, translation to SAT, etc.).  System descriptions should also
include a URL for a web site for the submitted tool.  System
descriptions may be submitted after the solver deadline, but to be
useful should be sent to the organizers before the competition ends.
We intend to make system descriptions publicly available.

>>>>

For participation in SMT-COMP, a solver must be uploaded to StarExec
and made publicly available.  StarExec supports solver configurations;
for clarity, \emph{each submitted solver must have one configuration
  only}.  Moreover, the organizers must be informed of the solver's
presence \emph{and the tracks and divisions in which it is
  participating} via the web form at
\begin{center}
  \todo{\url{}submission form url}
\end{center}
A submission must also include a \emph{system description} (see below) and a
\emph{32-bit unsigned integer}.
 These integer numbers, collected from all submissions, are used to seed the
benchmark scrambler.

\header{System description.}
%
As part of a submission, SMT-COMP entrants \emph{must} provide a short (1--2
pages) description of the system.
This should include a list of all authors of the system, their present
institutional affiliations, and any appropriate acknowledgements.  The
programming language(s) and basic SMT solving approach employed should
be described (e.g., lazy integration of a Nelson-Oppen combination
with SAT, translation to SAT, etc.).  System descriptions should also
include a URL for a web site for the submitted tool.  System
descriptions may be submitted after the solver deadline, but to be
useful should be sent to the organizers before the competition ends.
We intend to make system descriptions publicly available.
